method

### 2022-02-17 06_Paper/ER-ED/method.Rmd

# effect of valence on EMG

EMG_view <- data_EMG %>%
  subset(data_EMG$segment == "view_neu" | data_ER$block == "view_neg")
Ratings_view$block <- as.factor(Ratings_view$block)

>>>>

# effect of valence on EMG
# corrugator

EMG_view <- data_EMG %>%
  subset(data_EMG$block == "view_neu" | data_EMG$block == "view_neg")
EMG_view$block <- as.factor(EMG_view$block)

EMGCorrView_aov <- afex::aov_ez(data = EMG_view,
                               id = "ID",
                               dv = "Corr",
                               within = "block",
                               fun_aggregate = mean,
                               include_aov = TRUE)
